Supplementary Materials to ``Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic''

### 2022-03-21 write-up/covid-supplement-writeup.tex
New Figures for Supplement

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
 \centering
 \includegraphics[width=.9\linewidth]{../figs/tvprop_fig1.png}
 \caption{Testing Likelihood Given Fever and COVID-19 Contact}
 \label{fig:testinglik1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
 \centering
\includegraphics[width=.9\linewidth]{../figs/tvprop_fig2.png}
 \caption{Testing Propensity}
 \label{fig:testinglik2}
\end{subfigure}
\caption{Testing Likelihood Given no Fever nor COVID-19 Contact}
\label{fig:testinglik}
\end{figure}

@@

>>>>

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
 \centering
 \includegraphics[width=.9\linewidth]{../figs/tvprop_fig1.png}
 \caption{Testing Likelihood Given Fever and COVID-19 Contact}
 \label{fig:testinglik1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
 \centering
\includegraphics[width=.9\linewidth]{../figs/tvprop_fig2.png}
 \caption{Testing Likelihood Given Fever and COVID-19 Contact}
 \label{fig:testinglik2}
\end{subfigure}
\caption{Testing Likelihood Given no Fever nor COVID-19 Contact}
\label{fig:testinglik}
\end{figure}

@@

\subsubsection{Propensity plots}

Test

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
 \centering
 \includegraphics[width=.9\linewidth]{../figs/tvprop_alt_fig1_supp4.png}
 \caption{Symptom Likelihood Given Negative Test}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
 \centering
\includegraphics[width=.9\linewidth]{../figs/tvprop_alt_fig2_supp4.png}
 \caption{Symptom Likelihood Given Positive Test}
\end{subfigure}
\caption{Likelihood of COVID-19 contact for Non-Hispanic, White Females}
\end{figure}

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
 \centering
 \includegraphics[width=.9\linewidth]{../figs/tvprop_alt_fig1_supp1.png}
 \caption{Symptom Likelihood Given Negative Test}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
 \centering
\includegraphics[width=.9\linewidth]{../figs/tvprop_alt_fig2_supp1.png}
 \caption{Symptom Likelihood Given Positive Test}
\end{subfigure}
\caption{Likelihood of COVID-19 contact for Non-Hispanic, White Females}
\end{figure}

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
 \centering
 \includegraphics[width=.9\linewidth]{../figs/tvprop_alt_fig1_supp2.png}
 \caption{Symptom Likelihood Given Negative Test}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
 \centering
\includegraphics[width=.9\linewidth]{../figs/tvprop_alt_fig2_supp2.png}
 \caption{Symptom Likelihood Given Positive Test}
\end{subfigure}
\caption{Likelihood of COVID-19 contact for Non-Hispanic, White Females}
\end{figure}

\begin{figure}[!th]
\centering
\begin{subfigure}{.5\textwidth}
 \centering
 \includegraphics[width=.9\linewidth]{../figs/tvprop_alt_fig1_supp3.png}
 \caption{Symptom Likelihood Given Negative Test}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
 \centering
\includegraphics[width=.9\linewidth]{../figs/tvprop_alt_fig2_supp3.png}
 \caption{Symptom Likelihood Given Positive Test}
\end{subfigure}
\caption{Likelihood of COVID-19 contact for Non-Hispanic, White Females}
\end{figure}

\newpage
\subsubsection{Confidence Intervals}
